Containers and R---the Rockerverse and beyond

### 2020-01-10 manuscript.Rmd
fix footnote, no urldate for articles with DOI

The R-hub Docker images (see Section&nbsp;\ref{rhub}) can also be used to debug problems locally using various combinations of Linux platforms, R versions, and compilers\footnote{See \href{https://r-hub.github.io/rhub/articles/local-debugging.html}{https://r-hub.github.io/rhub/articles/local-debugging.html} and \href{https://blog.r-hub.io/2019/04/25/r-devel-linux-x86-64-debian-clang/}{https://blog.r-hub.io/2019/04/25/r-devel-linux-x86-64-debian-clang/}.
The images go beyond the configurations, or _flavours_, used by CRAN for checking packages\footnote{\href{https://cran.r-project.org/web/checks/check_flavors.html}{https://cran.r-project.org/web/checks/check_flavors.html}}, e.g., with CentOS-based images, but lack a container for checking on Windows or OS X.
The images greatly support package developers to provide support on operating systems they are not familiar.

>>>>

The R-hub Docker images (see Section&nbsp;\ref{rhub}) can also be used to debug problems locally using various combinations of Linux platforms, R versions, and compilers\footnote{See \href{https://r-hub.github.io/rhub/articles/local-debugging.html}{https://r-hub.github.io/rhub/articles/local-debugging.html} and \href{https://blog.r-hub.io/2019/04/25/r-devel-linux-x86-64-debian-clang/}{https://blog.r-hub.io/2019/04/25/r-devel-linux-x86-64-debian-clang/}.
The images go beyond the configurations, or _flavours_, used by CRAN for checking packages\footnote{\href{https://cran.r-project.org/web/checks/check_flavors.html}{https://cran.r-project.org/web/checks/check\_flavors.html}}, e.g., with CentOS-based images, but lack a container for checking on Windows or OS X.
The images greatly support package developers to provide support on operating systems they are not familiar.
